dynamics

### 2023-02-28 scripts/workshop/dynamics.Rmd
fix start params and knit

output_c <- as.data.frame(lsoda(xstart_n,times,rm0,params_c)) # tells computer to solve (integrate) equations
output_c1 <- as.data.frame(lsoda(xstart_n,times,rm1,params_c)) # tells computer to solve (integrate) equations

@@

output_a <- as.data.frame(lsoda(xstart_n,times,rm0,params_a)) # tells computer to solve (integrate) equations
output_a1 <- as.data.frame(lsoda(xstart_n,times,rm1,params_a)) # tells computer to solve (integrate) equations

@@

output_h <- as.data.frame(lsoda(xstart_n,times,rm0,params_h)) # tells computer to solve (integrate) equations
output_h1 <- as.data.frame(lsoda(xstart_n,times,rm1,params_h)) # tells computer to solve (integrate) equations

@@

output_x <- as.data.frame(lsoda(xstart_n,times,rm0,params_x)) # tells computer to solve (integrate) equations
output_x1 <- as.data.frame(lsoda(xstart_n,times,rm1,params_x)) # tells computer to solve (integrate) equations

@@

```{r}
ggplot()+
  geom_line(data=output_x,mapping = aes(y=I,x=time, color=color_x))+
  scale_color_manual(name="",values = "black")+
  new_scale_color()+
  geom_line(data=output_c, mapping=aes(y=I,x=time, color=color_c))+
  scale_color_manual(name="",values = "red")+
  new_scale_color()+
  geom_line(output_a, mapping=aes(y=I,x=time, color=color_a))+
  scale_color_manual(name="",values = "orange")+
  new_scale_color()+
  geom_line(output_h, mapping=aes(y=I,x=time, color=color_h))+
  scale_color_manual(name="",values = "purple")+
  new_scale_color()+
  geom_line(output_n, mapping=aes(y=I,x=time, color=color_n))+
  scale_color_manual(name="",values = "forestgreen")+
  labs(y="N",x="Time")+
  ylim(0,30)+
  ggtitle(paste("Total Infected Individuals (2 Species) Over Time Across Varying Conditions"))+
  theme_bw()
```

```{r}
ggplot()+
  geom_line(data=output_x1,mapping = aes(y=I,x=time, color=color_x))+
  scale_color_manual(name="",values = "black")+
  new_scale_color()+
  geom_line(data=output_c1, mapping=aes(y=I,x=time, color=color_c))+
  scale_color_manual(name="",values = "red")+
  new_scale_color()+
  geom_line(output_a1, mapping=aes(y=I,x=time, color=color_a))+
  scale_color_manual(name="",values = "orange")+
  new_scale_color()+
  geom_line(output_h1, mapping=aes(y=I,x=time, color=color_h))+
  scale_color_manual(name="",values = "purple")+
  new_scale_color()+
  geom_line(output_n1, mapping=aes(y=I,x=time, color=color_n))+
  scale_color_manual(name="",values = "forestgreen")+
  labs(y="N",x="Time")+
  ylim(0,30)+
  ggtitle(paste("Total Infected Individuals (2 Species) Over Time Across Varying Conditions w/o demo"))+
  theme_bw()
```

>>>>

xstart_c <- c(Sa=params_c[[6]]/params_c[[1]],
          Ia=1,
          Ra=0,
          Sb=params_c[[6]]/params_c[[2]],
          Ib=1,
          Rb=0,
          V=0)  # initial conditions

output_c <- as.data.frame(lsoda(xstart_c,times,rm0,params_c)) # tells computer to solve (integrate) equations
output_c1 <- as.data.frame(lsoda(xstart_c,times,rm1,params_c)) # tells computer to solve (integrate) equations

@@

xstart_a <- c(Sa=params_a[[6]]/params_a[[1]],
          Ia=1,
          Ra=0,
          Sb=params_a[[6]]/params_a[[2]],
          Ib=1,
          Rb=0,
          V=0)  # initial conditions

output_a <- as.data.frame(lsoda(xstart_a,times,rm0,params_a)) # tells computer to solve (integrate) equations
output_a1 <- as.data.frame(lsoda(xstart_a,times,rm1,params_a)) # tells computer to solve (integrate) equations

@@

xstart_h <- c(Sa=params_h[[6]]/params_h[[1]],
          Ia=1,
          Ra=0,
          Sb=params_h[[6]]/params_h[[2]],
          Ib=1,
          Rb=0,
          V=0)  # initial conditions

output_h <- as.data.frame(lsoda(xstart_h,times,rm0,params_h)) # tells computer to solve (integrate) equations
output_h1 <- as.data.frame(lsoda(xstart_h,times,rm1,params_h)) # tells computer to solve (integrate) equations

@@

xstart_x <- c(Sa=params_x[[6]]/params_x[[1]],
          Ia=1,
          Ra=0,
          Sb=params_x[[6]]/params_x[[2]],
          Ib=1,
          Rb=0,
          V=0)  # initial conditions

output_x <- as.data.frame(lsoda(xstart_x,times,rm0,params_x)) # tells computer to solve (integrate) equations
output_x1 <- as.data.frame(lsoda(xstart_x,times,rm1,params_x)) # tells computer to solve (integrate) equations

@@

```{r}
ggplot()+
  geom_line(data=output_x,mapping = aes(y=I,x=time, color=color_x))+
  scale_color_manual(name="",values = "black")+
  new_scale_color()+
  geom_line(data=output_c, mapping=aes(y=I,x=time, color=color_c))+
  scale_color_manual(name="",values = "red")+
  new_scale_color()+
  geom_line(output_a, mapping=aes(y=I,x=time, color=color_a))+
  scale_color_manual(name="",values = "orange")+
  new_scale_color()+
  geom_line(output_h, mapping=aes(y=I,x=time, color=color_h))+
  scale_color_manual(name="",values = "purple")+
  new_scale_color()+
  geom_line(output_n, mapping=aes(y=I,x=time, color=color_n))+
  scale_color_manual(name="",values = "forestgreen")+
  labs(y="N",x="Time")+
  ylim(0,40)+
  ggtitle(paste("Total Infected Individuals (2 Species) Over Time Across Varying Conditions"))+
  theme_bw()
```

```{r}
ggplot()+
  geom_line(data=output_x1,mapping = aes(y=I,x=time, color=color_x))+
  scale_color_manual(name="",values = "black")+
  new_scale_color()+
  geom_line(data=output_c1, mapping=aes(y=I,x=time, color=color_c))+
  scale_color_manual(name="",values = "red")+
  new_scale_color()+
  geom_line(output_a1, mapping=aes(y=I,x=time, color=color_a))+
  scale_color_manual(name="",values = "orange")+
  new_scale_color()+
  geom_line(output_h1, mapping=aes(y=I,x=time, color=color_h))+
  scale_color_manual(name="",values = "purple")+
  new_scale_color()+
  geom_line(output_n1, mapping=aes(y=I,x=time, color=color_n))+
  scale_color_manual(name="",values = "forestgreen")+
  labs(y="N",x="Time")+
  ylim(0,40)+
  ggtitle(paste("Total Infected Individuals (2 Species) Over Time Across Varying Conditions w/o demo"))+
  theme_bw()
```
